\documentclass{tccv}
\usepackage[english]{babel}
\usepackage{supertabular}
\usepackage{fontawesome}


% Command for entering a separate table row -- used as a generic visual element for any section that uses a two column table
\newcommand{\tableentry}[3]{
	\textsc{#1} & #2\expandafter\ifstrequal\expandafter{#3}{}{\\}{\\[6pt]} % First the heading, then content, then a conditional insertion of whitespace if the third parameter has any content in it
}

\begin{document}

\part{Mohammad Mahmoodian}

\section{Work Experience}

\begin{eventlist}

\item{March 2020}
	{Freelance}
	{Software Developer}

	Developed real-time people counting for the video stream, with help of computer vision and deep learning. Implemented Smart object detection and object tracking.

\item{August 2020}
	{Freelance}
	{Android Developer}

	Programmed a nordic Soc to capture data from an OSRAM Opto Semiconductor (SFH7070). Developed an app in Android Studio to communicate with the nRF through the BLE and display the captured data.

%\item{August 2020}
%{Freelance}
%{Software and Hardware Development}
%
%Programming a nordic nRF52840 Soc to capture data from an OSRAM Opto Semiconductor (SFH7070). Developing an app in Android Studio to communicate with the nRF through the BLE and display the captured data.


\item{September 2019 -- Present}
     {PAD Lab, UTSTPark, Tehran, Iran}
     {Blockchain Developer}
     
	Work with popular cryptocurrency source codes at \href{www.padlab.ir}{PAD} (Processing and Analysis Data) lab under the supervision of \href{www.mahsan.co}{Mahsan Co.} in the \href{www.utstpark.ir}{UTSTPark} (University of Tehran Science and Technology Park).

%\item{March 2019 -- September 2019}
%     {Datis, Tehran, Iran}
%     {Hardware Development}
%
%Hardware programming for STM32 Arm Cortex MCUs and development of elevator drives at \href{www.datis-elevator.ir}{Datis Elevator}.

%\item{February 2017 -- Present}
%     {MCS Lab in the University of Tehran}
%     {Software Development and Research Assistance}
%
%	Worked with Linux-based operating systems (e.g., OpenWrt) and installed them on Wi-Fi routers.

\item{December 2017 -- January 2019}
     {Farineh Fanavar, Tehran, Iran}
     {Software Developer}

	Implemented IoT protocols using blockchain and smart contracts. Worked with tools such as truffle and Geth (Go Ethereum) to test and simulate smart grids at \href{http://farinehtech.com/}{Farineh Fanavar}.

\end{eventlist}

\section{Education}
\begin{yearlist}
	\item[Master of Science]{2017 -- 2020}
	{Electrical Engineering - Network Communications}
	{University of Tehran\newline GPA: 18.8 \newline Rank: 1}
	
	\item[Bachelor of Science]{2013 -- 2017}
	{Electrical Engineering - Communications}
	{University of Tehran.\newline GPA: 18.4 \newline Rank: 8}
\end{yearlist}

\section{Selected Courses}
\begin{tabular}{ll}
	Pattern Recognition ($\frac{19.2}{20}$)	&Advanced Programming ($\frac{18}{20}$) \\
	Data Networks ($\frac{20}{20}$)			&Distributed Optimization ($\frac{18.5}{20}$) \\
	Stochastic Processes ($\frac{19}{20}$)	&Cellar Networks ($\frac{20}{20}$)
\end{tabular}

\personal
    [www.linkedin.com/in/mohammad-mahmoodian-397a508a]
    {Tehran, Iran}
    {+98 (938) 3172746}
    {mahmoodian@ut.ac.ir}
    {www.github.com/momaee}

\section{Projects}

\begin{yearlist}
\item{2020}
{OpenCV}
	{Implemented a real-time people counter using OpenCV, SciPy, etc. in Python language programming.}

\item{2020}
	{Android Studio}
	{Developed an app in Android Studio using Java programming language to connect to a device through BLE and display received data.}

\item{2020}
	{Nordic nRF}
	{Worked with Nordic nRF52840 SoC and programming the chip, in C programming language using Keil IDE.}

%\item{2020}
%	{NEO Cryptocurrency}
%	{Edit NEO client source code in C\# programming language.}

\item{2020}
	{TON Cryptocurrency}
	{Edited TON (Telegram Open Network) client source code and added some features to it.}

\item{2019}
     {Geth}
     {Work with Go-Ethereum (official Go implementation of Ethereum protocol) and add some features to it (e.g. writing data onto CassandraDB, Neo4jDB, LevelDB, etc.).}

%\item{2019}
%     {STM32 MCUs}
%     {Embedded devices programmer. MCU programming in Keil.}

\item{2018}
     {Smart Contract}
     {Built smart contracts using solidity and hyperledger sawtooth. used web3 Restful api in Python and JavaScript to connect to blockchain.}

\item{2018}
     {Zigbee}
     {Implemented Zigbee protocol on XBee modules using Keil.}

\item{2017}
     {OpenWrt}
     {Installation of OpenWrt on routers.}
\end{yearlist}
%\textbf{\\ \\ \\}


\section{Computer Skills}
\begin{factlist}

\item{Good level}
     {Python, OpenCV, NumPy, SciPy, Scikit-learn, MNIST, SVM, Go, C, C++, C\#, Java, Cryptocurrency, Database}

%\item{Good level}
%	{Python, OpenCV, NumPy, SciPy, Scikit-learn, MNIST, SVM, Go, Solidity, C, C++, C\#, Java, Android Studio, git, Cryptocurrency, Linux, Restful APIs, IP Networking, Matlab, Neo4j Database, LevelDB, Cassandra Database, MongoDB}

\item{Intermediate}
     {Hyperledger, \LaTeX, Keil, Wireshark, shell, Node.js, HTML, JavaScript}

%\item{Basic level}
%     {Windows, Microsoft Word}

\end{factlist}

%\section{Communication Skills}
%\begin{factlist}
%	\item{Persian}{Native speaker}
%	\item{English}{Good}
%\end{factlist}

%\section{References}  
%\begin{supertabular}{rl}
%		
%	\tableentry{}{\textbf{\href{https://ece.ut.ac.ir/en/~bahrak}{Dr. Behnam Bahrak}}}{}
%	\tableentry{Position}{Assistant Professor}{}
%	\tableentry{}{\href{http://ece.ut.ac.ir/en}{School of Electrical and Computer Engineering}}{}
%	\tableentry{}{\href{https://ut.ac.ir/en}{\textit{University of Tehran}}}{}
%	%  \tableentry{Email}{\href{mailto:m.davarpanah@ut.ac.ir}{m.davarpanah@ut.ac.ir}}{}
%	
%	\tableentry{}{\textbf{\href{https://ece.ut.ac.ir/en/~vmansouri}{Dr. Vahid Shahmansouri}}}{}
%	\tableentry{Position}{Assistant Professor}{}
%	\tableentry{}{\href{http://ece.ut.ac.ir/en}{School of Electrical and Computer Engineering}}{}
%	\tableentry{}{\href{https://ut.ac.ir/en}{\textit{University of Tehran}}}{}
%	%  \tableentry{Email}{\href{mailto:vmansouri@ut.ac.ir}{vmansouri@ut.ac.ir}}{spaceafter}
%	
%	\tableentry{}{\textbf{\href{https://www.linkedin.com/in/masih-nilchian/?originalSubdomain=ch}{Dr. Masih Nilchian}}}{}
%	\tableentry{Position}{Chief Technology Officer}{}
%	\tableentry{}{\href{https://mypulses.com/}{MyPulses Co.}}{}
%%	\tableentry{}{\href{https://ut.ac.ir/en}{\textit{University of Tehran}}}{}
%	%  \tableentry{Email}{\href{mailto:}{}}{}
%	
%	 \tableentry{}{\textbf{\href{https://ece.ut.ac.ir/en/~araabi}{Dr. Babak Nadjar Araabi}}}{}
%	\tableentry{Position}{Professor}{}
%	\tableentry{}{\href{http://ece.ut.ac.ir/en}{School of Electrical and Computer Engineering}}{}
%	\tableentry{}{\href{https://ut.ac.ir/en}{\textit{University of Tehran}}}{}
%	%  \tableentry{Email}{\href{mailto:}{}}{}
%\end{supertabular}

\end{document}
